Supplemental material for Tree growth, mortality, and climatic stress in west-coast states, USA

### 2025-11-03 Supplemental Material.Rmd
Latest version of manuscript, added CWD analysis to supplemental materials.

source('Global.R')
source(paste0(CODE.LOC, "Functions.R"))
# Some general analysis info + plots
analysis.stats <- read_rds(paste0(RESULTS.OTHER, "analysis.stats.RDS"))

@@

```{r cwd_summary_tables}
cwd.init <- analysis.stats$init.cwd.stats 
cwd.diff <- analysis.stats$diff.cwd.stats

@@

```{r table-legends}
tab_nums <- captioner::captioner(prefix = "Table S")

@@

@@

>>>>

source('Global.R')
source(paste0(CODE.LOC, "Functions.R"))
# Some general analysis info + plots
analysis.stats <- read_rds(paste0(RESULTS.OTHER, "analysis.stats.RDS"))
# Correlation/fits for Initial CWD vs Delta CWD:
CWD.rels <- read_rds(paste0(RESULTS.OTHER, "CWD_deltaCWD_relationship.rds"))

@@

```{r cwd_summary_tables}
ft.lm1 <- CWD.rels$ft_lm1

cwd.init <- analysis.stats$init.cwd.stats 
cwd.diff <- analysis.stats$diff.cwd.stats

@@

```{r legends}
fig_nums <- captioner::captioner(prefix = " S")
tab_nums <- captioner::captioner(prefix = "Table S")

f.ref <- function(x) {
 caption_text <- fig_nums(x)
  # Remove any leading numbers and extract just "Figure X"
  stringr::str_extract(caption_text, "\\d+")
}

@@

tbl_cwd_lm1 <- tab_nums(name = "tbl_cwdlm1", 
                         caption = "Linear regression model output for the linear fit of initial and delta CWD plot data (green line in Figure S1). Variable name CWD refers to initial CWD value.")

tbl_cwd_lm2 <- tab_nums(name = "tbl_cwdlm2", 
                         caption = "Linear regression model output for the third-order polynomial fit of initial and delta CWD plot data (orange line in Figure S1). Variable name CWD refers to initial CWD value.")

@@

fig_cwd_all <- fig_nums(name = "fig_cwdall", 
                        caption = "Initial CWD and Delta CWD values for all FIA plots occupied by analysis species. The green line is a linear fit of the values while the orange line is a third-order polynomial fit of the points.  ")

fig_cwd_spp <- fig_nums(name = "fig_cwdspp", 
                        caption = "Third-order polynomial fits for initial CWD and delta CWD values for FIA plots occupied by individual species.")

<br>

<br>

```{r cwdfig-all, fig.width=6, fig.height=6,  fig.dpi=300, fig.cap=fig_cwd_all, fig.cap.sep=""}

# Output from Nplot_Climvar_analysis.R
knitr::include_graphics(paste0(RESULTS.OTHER, "CWD_deltaCWD.png"))

```{r table-cwd-lm1, tab.cap=tbl_cwd_lm1}

# Output from Nplot_Climvar_analysis.R
#ft.lm1.1 <- ft.lm1 %>%
#  compose(i = 2, j = 1, value = as_paragraph("CWD"), part = "body")

ft.lm1.1 <- ft.lm1 %>%
     mk_par(i = 2, j = 1, value = as_paragraph("CWD"), part = "body")

ft.lm1.1

<br>

<br>

```{r table-cwd-lm2, tab.cap=tbl_cwd_lm2}

# Output from Nplot_Climvar_analysis.R
ft.lm2 <- CWD.rels$ft_lm2 %>%
 set_formatter(
      values = function(y) formatC(y, format = "e", digits = 2),
      part = "body"
    ) %>%
  mk_par(i = 2:4, j = 1, value = c(as_paragraph("CWD"), as_paragraph("CWD^2"), as_paragraph("CWD^3")), part = "body")

ft.lm2

```{r cwdfig-spp, fig.width = 6, fig.height= 6,  fig.dpi=300, fig.cap=fig_cwd_spp, fig.cap.sep=""}

# Output from Nplot_Climvar_analysis.R
knitr::include_graphics(paste0(RESULTS.OTHER, "CWD_spp_plt.png"))
